---
title: "Collect and Clean SPLT Data"
author: "John Flournoy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Data from the Social Probabilistic Learning Task was collected from 5 different samples: Community adolescents, foster-care involved adolescents, at-risk adolescents, University of Oregon human subject pool (UOHSP) particupants who visitied the lab, and UOHSP participants who completed the study online. Data is excluded for any participant who did failed showed a pattern of inattentive responding on the questionnaires and who generated response times that are inconsistent with attentive responding during the task.

List of unexcused no-show IDs (these will be excluded):

- 38547
- 44123
- 43237
- 42283
- 43873

List of IDs with errors in output files (incomplete file save; will be included but sensitivity to inclusion will be assessed):

- 43993
- 43640
- 43329
- 43303
- 40179

Other issues to check:

- YADS 386 has two output files.
- YADS_online 43603 has two output files.
- 43991
- 43214



```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

anon_id_filename <- '/data/jflournoy/split/splt_anon_id.csv'
```

```{r}
library(dplyr)
library(tidyr)
library(readr)
library(stringr)

root_dir <- '~/code_new/probly/extdata/' # This would be '/Volumes/' if you've mounted locally
raw_data_dir <- file.path(root_dir, 'raw/')
processed_data_dir <- file.path(root_dir, 'processed/')
conditions <- c('HungryThirsty', 'DatingLooking', 'PopularUnpopular')
metacog_condition <- 'Confidence'
file_match_pattern <- 'split.*csv'

col_spec <- readr::cols(
    .default = readr::col_character(),
    rt = readr::col_integer(),
    key_press = readr::col_integer(),
    trial_index = readr::col_integer(),
    time_elapsed = readr::col_integer(),
    block_duration = readr::col_integer(),
    timing_post_trial = readr::col_integer(),
    correct_response = readr::col_integer(),
    possible_responses = readr::col_number(),
    stim_duration = readr::col_integer(),
    feedback_duration = readr::col_integer(),
    optimal_response = readr::col_integer(),
    stimindex = readr::col_integer(),
    reward_possible = readr::col_integer(),
    stim_chosen = readr::col_integer(),
    qnum = readr::col_integer(),
    page_num = readr::col_integer(),
    trial_num = readr::col_integer(),
    score_response = readr::col_integer(),
    response_range = readr::col_number(),
    times_viewed = readr::col_integer()
)

files <- dplyr::data_frame(file = dir(path = raw_data_dir, 
                                      pattern = file_match_pattern,
                                      recursive = T)) 

message(paste0('Files: ', length(unique(files$file))))

parsed_filenames <- tidyr::extract(
    files, 
    file, c('filename', 'dir', 'id', 'timestamp'), 
    '(([\\w]+/)*split-([0-9]+|bad_pid)[-_]([0-9]+)\\.csv)')

splt_data_and_problems <- do(
    dplyr::group_by(
        parsed_filenames,
        filename, dir, id, timestamp),
    {
        adf = readr::read_csv(file.path(raw_data_dir, .$filename[[1]]), col_types = col_spec)
        prob_adf <- dplyr::mutate_all(problems(adf), funs(as.character))
        data_frame(data = list(adf), problems = list(prob_adf))
    })

splt_data_and_problems$.id <- as.character(1:dim(splt_data_and_problems)[1])
names(splt_data_and_problems$data) <- splt_data_and_problems$.id
names(splt_data_and_problems$problems) <- splt_data_and_problems$.id

splt_data <- left_join(
    bind_rows(splt_data_and_problems$data, .id = '.id'),
    splt_data_and_problems[,c('.id', 'filename', 'dir', 'id', 'timestamp')])
splt_problems <- left_join(
    bind_rows(splt_data_and_problems$problems, .id = '.id'),
    splt_data_and_problems[,c('.id', 'filename', 'dir', 'id', 'timestamp')])

splt_crunched <- splt_data %>%
    dplyr::filter((trial_id == 'stim' & (key_press>0 | key_press==-1)) | (trial_id == 'metacog')) %>%
    tidyr::extract(image, 
                   c('stim_image', 'sex'), 
                   '.*/(([fma])_f42887_e_[0-9]{3}\\.png)') %>%
    dplyr::mutate(correcttrue = ifelse(key_press == -1, NA, as.numeric(correct == 'true')),
                  outcome = ifelse(feedback, reward_possible, 0),
                  pressed_r = c(`37` = 0,`39` = 1)[as.character(key_press)],
                  correct_r = c(`37` = 0,`39` = 1)[as.character(correct_response)]) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(proportion = condition, 
                  condition = paste(sort(unlist(str_split(context, '_'))), collapse = ''), 
                  condition = ifelse(trial_id == 'metacog', 'Confidence', condition),
                  correcttrue = ifelse(trial_id == 'metacog', 
                                     as.numeric(score_response), correcttrue)) %>%
    dplyr::filter(condition %in% c(conditions, metacog_condition)) %>%
    dplyr::group_by(filename, id, condition) %>%
    dplyr::mutate(condition_trial_index = 1:n(),
                  block = ((condition_trial_index-1) %/% 16) + 1,
                  dir = ifelse(is.na(dir), '/', dir),
                  sample = ifelse(dir %in% c('yads/', 'yads_online/'),
                                  sub('/', '', dir),
                                  c('TDS2', 'TDS2', 'TDS1', 'TDS3')[floor(as.numeric(id)/100)])) %>%
    dplyr::ungroup() %>%
    dplyr::select(id, dir, filename, sample,
                  correcttrue, pressed_r, outcome, 
                  correct_r, reward_possible,
                  condition, condition_trial_index, 
                  sex, stim_image, 
                  trial_index, block, proportion, 
                  rt, time_elapsed)

participant_anon_id <- readr::read_csv(file = anon_id_filename)
splt_crunched <- dplyr::left_join(splt_crunched, unique_participants, by = c('id', 'sample'))
splt_crunched <- dplyr::mutate(splt_crunched, id = anon_id, sample = anon_sample)
splt_crunched <- dplyr::select(splt_crunched, -anon_id, -anon_sample)

metacog_clean <- splt_crunched %>% 
    dplyr::select(-sex, -stim_image) %>%
    dplyr::filter(condition == metacog_condition,
                  !is.na(correcttrue)) %>%
    dplyr::mutate(block=(condition_trial_index+1)/2) %>% 
    tidyr::spread(condition, correcttrue) %>%
    dplyr::rename(confidence=Confidence) %>%
    dplyr::select(sample, id, block, confidence)

splt_clean <- splt_crunched %>% 
    dplyr::filter(condition != metacog_condition) %>%
    dplyr::mutate(condition = factor(condition, 
                                     levels = conditions, 
                                     labels = abbreviate(conditions))) %>%
    dplyr::arrange(sample, id, trial_index)

```


```{r eval=F}
#Write the data
splt <- splt_clean
splt_confidence <- metacog_clean
devtools::use_data(splt, splt_confidence)
```
