---
title: "Descriptive Statistics for SPLT data"
author: "John Flournoy"
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: yes
    toc_depth: 2
    number_sections: FALSE
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = F, error = F,warning = F, echo = F,
  comment = "#>"
)
```

# Participants

Data from four samples are used in this analysis. 
The first two samples comprise foster-care-involved and community adolescents who were recruited from the greater Eugene/Springfield area for an ongoing longitudinal study investigating decision-making related to health-risking behavior (NIH grant number:). 
The third and forth samples consisted of college students who completed the study for course credit either in person, or online. 
Some participants in each sample did not provide data on all focal measures (see Table \@ref:missingstats), and so sample sizes for each analysis will differe to some extent.
Examining the table, it is clear that the proportion of missing data is small.

in table \@ref(tab:samplestats)

(ref:samplestats) (\#tab:samplestats) Descriptive statistics on age, and PDSS for each sample

(ref:missingstats) (\#tab:missingstats) Missing data from each sample for age, PDSS, and gender

(ref:optpressstats) (\#tab:optpressstats) Probability that an optimal choice results in reward

(ref:ethnicitytable) (\#tab:ethnicitytable) Race/ethnicity information by sample


```{r load_packages_and_data}
library(probly)
library(dplyr)
library(tidyr)
library(ggplot2)
data('splt', 'splt_confidence', 'splt_dev_and_demog')

sample_labels <- c(
    'TDS1' = 'Foster-care involved adolescents',
    'TDS2' = 'Community adolescents',
    'yads' = 'College students',
    'yads_online' = 'College students - online'
)

condition_labels <- c(
    'HngT' = 'Hungry/Thirsty',
    'DtnL' = 'Dating/Looking', 
    'PplU' = 'Popular/Unpopular'
)

ethnicity_labels <- c(
    'American Indian and Alaska Native' = 'AmIndn',
    'Asian' = 'Asian',
    'Black or African American' = 'Black/AA',
    'Latinx/Hispanic' = 'Latinx/Hsp',
    'Native Hawaiian and Other Pacific Islander' = 'Pcfc Islnd',
    'Other' = 'Other',
    'White' = 'White',
    'White/Hispanic' = 'Wht/Hsp'
)

splt$condition <- factor(splt$condition, levels = names(condition_labels), labels = condition_labels)
splt$sample <- factor(splt$sample, levels = names(sample_labels), labels = sample_labels)
splt_dev_and_demog$sample <- factor(splt_dev_and_demog$sample, levels = names(sample_labels), labels = sample_labels)
splt_dev_and_demog$gender <- factor(splt_dev_and_demog$gender, levels = c(0, 1), labels = c('Male', 'Female'))
splt_dev_and_demog$ethnicity <- factor(splt_dev_and_demog$ethnicity, levels = names(ethnicity_labels), labels = ethnicity_labels)
```

```{r summary, results='asis'}
library(tables)
writeCSS(CSS = htmloptions()$CSS)
mean.na.rm <- function(x){mean(as.numeric(x), na.rm=T)}
sd.na.rm <- function(x){sd(x, na.rm=T)}
nmissing <- function(x){m <- sum(is.na(x));ifelse(m==0,'-',m)}
prct_missing <- function(x,y){pct <- 100*sum(is.na(x))/length(y);ifelse(pct==0,'\\-',pct)}

splt_did_task <- dplyr::summarize(
    dplyr::group_by(splt, id, sample),
    ntrials = sum(!is.na(pressed_r))
)

splt_dev_and_demog_task_sum <- dplyr::full_join(
    splt_dev_and_demog,
    splt_did_task,
    by = c('SID' = 'id', 'sample')
)

splt_dev_and_demog_task_sum$gender_num <- as.numeric(splt_dev_and_demog_task_sum$gender)

splt_by_cond_samp <- dplyr::group_by(splt, condition, sample)
splt_summary_optimal_feedback <- dplyr::summarize(
    splt_by_cond_samp,
    p_optimal_correct = mean((proportion == '20_80') == (correct_r == 1))
)


sample_table <- tables::tabular(
    (Sample=sample) ~ 
        (N = 1)*Heading()*(gender) +
             ((Format(digits=1)*(Age = age) + 
                   Format(digits=1)*(PDSS = PDSS_pdss) + 
                   Format(digits=0)*(`N~trials~` = ntrials))*Heading()*(gender)*
                  ((M = mean.na.rm) + 
                       (`SD` = sd.na.rm))), 
    data = splt_dev_and_demog_task_sum)

missing_table <- tables::tabular(
    ((Sample=sample) + 1) ~ 
        (N=1) +
             (((Age=age) + (PDSS=PDSS_pdss) + (Gender = gender_num) + (Task = ntrials))*
                  ((`N~miss~` = nmissing) + Format(digits=1)*(`%` = Percent(fn = prct_missing)))), 
    data = splt_dev_and_demog_task_sum)

optimal_press_prop_table <- tables::tabular((Condition = condition)*(Sample = sample) ~ 
                    Heading('Probability of reward')*
                    identity*Heading()*Format(digits=3)*p_optimal_correct, 
                data = splt_summary_optimal_feedback)
ethnicity_table <- tables::tabular(
    Heading('Percent (%)')*ethnicity*Heading()*Format(digits=1)*Percent() ~
        1 + Heading()*(Sample = sample),
    data = splt_dev_and_demog_task_sum)
```

```{r missingstats}
html(missing_table, 
     options = list(
         justification = c('l'), 
         rowlabeljustification = c('l'), 
         pad = TRUE,
         HTMLcaption = '(ref:missingstats)'))
```

```{r samplestats}
html(sample_table, 
     options = list(
         justification = c('l'), 
         rowlabeljustification = c('l'), 
         pad = TRUE,
         HTMLcaption = '(ref:samplestats)'))
```

```{r ethnicitytable}
html(ethnicity_table, 
     options = list(
         justification = c('r'), 
         rowlabeljustification = c('l'), 
         pad = TRUE,
         HTMLcaption = '(ref:ethnicitytable)'))
```

```{r optpressstats}
html(optimal_press_prop_table, 
     options = list(
         justification = c('l'), 
         rowlabeljustification = c('l'), 
         pad = TRUE,
         HTMLcaption = '(ref:optpressstats)'))
```





<!-- ```{r reaction_time, fig.width=10.5, fig.height=8, cache=T} -->
<!-- ggplot2::ggplot( -->
<!--     dplyr::filter(splt, rt > 0), -->
<!--     ggplot2::aes(x = rt/1000)) +  -->
<!--     ggplot2::geom_vline(xintercept = 1, size = .5, color = '#666666') +  -->
<!--     ggplot2::geom_histogram(binwidth = .1, fill = 'black') + -->
<!--     ggplot2::theme_minimal() +  -->
<!--     ggplot2::theme(strip.background = element_blank(),  -->
<!--                    strip.text = element_blank()) +  -->
<!--     ggplot2::scale_x_continuous(breaks = c(0, 1, 2)) + -->
<!--     facet_wrap(~id, ncol = 20) +  -->
<!--     coord_cartesian(x = c(0, 2)) + -->
<!--     labs(x = 'Trial reaction-time (s)',  -->
<!--          y = 'Count', -->
<!--          title = 'Reaction time for all participants') -->

<!-- max_number_of_trials <- max( -->
<!--     dplyr::summarise( -->
<!--         dplyr::group_by( -->
<!--             dplyr::filter(splt, !is.na(pressed_r)),  -->
<!--             id, condition), -->
<!--         n_trials = n())$n_trials -->
<!--     ) -->

<!-- ggplot2::ggplot( -->
<!--     dplyr::filter(splt, !is.na(pressed_r)), -->
<!--     ggplot2::aes(x = condition)) +  -->
<!--     ggplot2::geom_hline(yintercept = max_number_of_trials, color = '#666666') +  -->
<!--     ggplot2::geom_bar(fill = '#bbbbbb') + -->
<!--     ggplot2::theme_minimal() +  -->
<!--     ggplot2::theme(strip.background = element_blank(), -->
<!--                    strip.text = element_blank(), -->
<!--                    axis.text.x = element_text(angle = 360-45, hjust = 0)) + -->
<!--     facet_wrap(~id, ncol = 20) +  -->
<!--     labs(x = 'Condition',  -->
<!--          y = paste0('Number of trials (line at max = ', max_number_of_trials, ')'), -->
<!--          title = 'Trials per condition for all participants') -->
<!-- ``` -->

<!-- # Raw task data -->

<!-- Averaging over trials -->

<!-- ```{r fig.width=7, fig.height=6, cache=T} -->

<!-- splt_averages <- splt %>% -->
<!--     dplyr::group_by(sample, condition, condition_trial_index) %>% -->
<!--     dplyr::summarize(p_optimal = mean(correcttrue, na.rm = T)) %>% -->
<!--     dplyr::ungroup() -->

<!-- splt_averages_over_samples <- splt %>% -->
<!--     dplyr::group_by(condition, condition_trial_index) %>% -->
<!--     dplyr::summarize(p_optimal = mean(correcttrue, na.rm = T)) %>% -->
<!--     dplyr::ungroup() -->

<!-- ggplot2::ggplot( -->
<!--     splt_averages, -->
<!--     ggplot2::aes(x = condition_trial_index, -->
<!--                  y = p_optimal, -->
<!--                  group = condition, -->
<!--                  linetype = condition, -->
<!--                  shape = condition)) +  -->
<!--     ggplot2::geom_point(alpha = .1) +  -->
<!--     ggplot2::geom_smooth( -->
<!--         color = 'black', size = .5, -->
<!--         method = 'gam', formula = y ~ s(x, bs = "cs", k = 8), se = T) +  -->
<!--     ggplot2::facet_wrap(~sample, nrow = 2) +  -->
<!--     ggplot2::labs(x = 'Within-condition trial number', -->
<!--                   y = 'Proportion of optimal responses') +  -->
<!--     ggplot2::theme_minimal() -->

<!-- ggplot2::ggplot( -->
<!--     splt_averages_over_samples, -->
<!--     ggplot2::aes(x = condition_trial_index, -->
<!--                  y = p_optimal, -->
<!--                  group = condition, -->
<!--                  linetype = condition, -->
<!--                  shape = condition)) +  -->
<!--     ggplot2::geom_point(alpha = .1) +  -->
<!--     ggplot2::geom_smooth( -->
<!--         color = 'black', size = .5, -->
<!--         method = 'gam', formula = y ~ s(x, bs = "cs", k = 8), se = T) + -->
<!--     ggplot2::labs(x = 'Within-condition trial number', -->
<!--                   y = 'Proportion of optimal responses') +  -->
<!--     ggplot2::theme_minimal() -->


<!-- ``` -->

<!-- Self-reported confidence over blocks -->

<!-- ```{r fig.width=6, fig.height=4, cache=T} -->
<!-- ggplot2::ggplot( -->
<!--     dplyr::filter(splt_confidence, !is.na(sample), sample != 'TDS3'), -->
<!--     ggplot2::aes(x = block, y = confidence)) +  -->
<!--     ggplot2::geom_point(position = ggplot2::position_jitter(w = .3, h = .3), alpha = .1) + -->
<!--     ggplot2::geom_smooth( -->
<!--         ggplot2::aes(color = sample), -->
<!--         method = 'gam', formula = y ~ s(x, bs = "cs", k = 8), se = F) +  -->
<!--     ggplot2::theme_minimal() +  -->
<!--     ggplot2::labs(x = 'Block number', -->
<!--                   y = 'Self-report confidence about optimal label') -->
<!-- ``` -->

<!-- # Proportion optimal presses per ID & condition -->

<!-- ```{r cache=T} -->
<!-- plot_opt_presses_per_id <- function(splt_df,  -->
<!--                                     ncol = 5,  -->
<!--                                     title = 'Proportion optimal presses per ID & condition', -->
<!--                                     se = F){ -->
<!--     splt_opt_press <- dplyr::mutate( -->
<!--         ungroup(splt_df),  -->
<!--         press_opt = as.numeric(pressed_r == (proportion == '20_80')), -->
<!--         press_opt = (press_opt - .5) * (1 -.05 * (as.numeric(condition) - 1)) + .5) -->

<!--     splt_opt_press_ranks <- dplyr::summarize( -->
<!--         dplyr::group_by(splt_opt_press, id), -->
<!--                         mean_press_opt = mean(press_opt, na.rm = T)) -->
<!--     splt_opt_press_ranks$id_fac <- factor( -->
<!--         splt_opt_press_ranks$id, -->
<!--         levels = splt_opt_press_ranks$id[order(splt_opt_press_ranks$mean_press_opt)]) -->

<!--     splt_opt_press <- left_join(splt_opt_press, splt_opt_press_ranks) -->

<!--     ggplot2::ggplot( -->
<!--         splt_opt_press,  -->
<!--         ggplot2::aes( -->
<!--             x = condition_trial_index,  -->
<!--             y = press_opt, -->
<!--             linetype = condition, -->
<!--             shape = condition)) + -->
<!--         ggplot2::geom_point(size = .75, alpha = .25) +  -->
<!--         ggplot2::geom_hline(yintercept = c(.8), alpha = 1, color = 'red', size = .5) +  -->
<!--         ggplot2::geom_hline(yintercept = c(.5), alpha = 1, color = 'gray', size = .5) +  -->
<!--         ggplot2::geom_smooth(se = se, method = 'gam', formula = y ~ s(x, bs = "tp", k = 4),  -->
<!--                              size = .5, color = 'black', alpha = .2) +  -->
<!--         ggplot2::facet_wrap(~ id_fac, ncol = ncol) + -->
<!--         ggplot2::coord_cartesian(ylim = c(0, 1)) +  -->
<!--         ggplot2::scale_y_continuous(breaks = c(0,.5,.8)) +  -->
<!--         ggplot2::scale_x_continuous(breaks = c(1,64,128)) + -->
<!--         ggplot2::theme_minimal() + -->
<!--         ggplot2::labs(x = 'Trial', y = 'Optimal press (probability)', title = title) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r proportion_trials_per_conditionca, fig.width=10, fig.height=22, cache=T} -->
<!-- plot_opt_presses_per_id( -->
<!--     dplyr::filter(splt, sample == 'Community adolescents'), -->
<!--     ncol = 5,  -->
<!--     title = 'Community adolescents') -->
<!-- ``` -->

<!-- ```{r proportion_trials_per_conditionfc, fig.width=10, fig.height=10, cache=T} -->
<!-- plot_opt_presses_per_id( -->
<!--     dplyr::filter(splt, sample == 'Foster-care involved adolescents'), -->
<!--     ncol = 5,  -->
<!--     title = 'Foster-care involved adolescents') -->
<!-- ``` -->

<!-- ```{r proportion_trials_per_conditioncs, fig.width=10, fig.height=22, cache=T} -->
<!-- plot_opt_presses_per_id( -->
<!--     dplyr::filter(splt, sample == 'College students'), -->
<!--     ncol = 5,  -->
<!--     title = 'College students') -->
<!-- ``` -->

<!-- ```{r proportion_trials_per_conditioncso, fig.width=10, fig.height=44, cache=T} -->
<!-- plot_opt_presses_per_id( -->
<!--     dplyr::filter(splt, sample == 'College students - online'), -->
<!--     ncol = 5,  -->
<!--     title = 'College students - online') -->

<!-- ``` -->
