---
title: "Test Simple 3-level Multivariate Normal Model"
author: "John Flournoy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Generate data where there are 3 conditions, and individual variation in probability of choosing 'left' for each condition. Set the mean probability of left for each condition to values in `beta_mu` below.

```{r}
set.seed(150319/2018)
j <- 300 #number of subjects
t <- 100 #number of trials
g <- 4 #number of subsamples
c <- 3 #number of conditions
n <- t*c*j #number of observations
gg <- sample(1:g, size = j, replace = T) #group IDs

hyper_gamma_mu <- c(-1, 0, 1) #The mean population effect
hyper_gamma_sigma <- 1
gamma_mu <- matrix(rnorm(c*g, hyper_gamma_mu, hyper_gamma_sigma), nrow = g, byrow = T) #specific sample mean effects
gamma_sigma <- matrix(
    c(1, .2, .2,
      .2, 1, .2,
      .2, .2, 1),
    nrow = 3, byrow = T
) #correlation among random effects at between individuals in the same sample

beta_j <- t(apply(gamma_mu[gg,], 1, function(mu) {MASS::mvrnorm(1, mu, gamma_sigma)}))

beta_j_df <- as.data.frame(beta_j)
beta_j_df$b0 <- beta_j_df[,1]
beta_j_df$b1 <- beta_j_df[,2] - beta_j_df[,1]
beta_j_df$b2 <- beta_j_df[,3] - beta_j_df[,1]

summary(beta_j_df)
cor(beta_j_df[,1:3])
cor(beta_j_df[,4:6])

lapply(1:g, function(grp) cor(beta_j_df[gg == grp,1:3]))

dd <- data.frame(id = as.factor(1:j),
                 grp = as.factor(gg),
                 condition = as.factor(rep(rep(1:3, each = n/j/3), each = j)))

design <- model.matrix(~ 0 + id:condition, dd)

dd$theta <-  design %*% as.vector(beta_j)

dd$p <- arm::invlogit(dd$theta)
dd$y <- rbinom(dim(dd)[1], 1, dd$p)

dplyr::summarize(
    dplyr::group_by(dd, grp), 
    N = length(unique(id)))
```

```{r}
library(lme4)
library(brms)
library(rstan)
library(future)
plan('multiprocess')

glm_fit <- glm(y ~ 1 + condition, data = dd, family = 'binomial')

lme4_fit_fn <- '/data/jflournoy/split/probly/lme4_test_fit.RDS'
lme4_fit_future <- future::future(
    CachedFit(
        {
            lme4::glmer(y ~ 1 + condition + (1 + condition | grp/id), data = dd, family = 'binomial')
        },
        rds_filename = lme4_fit_fn))

lme4_fit_2L_fn <- '/data/jflournoy/split/probly/lme4_test_fit_2L.RDS'
lme4_fit_2L_future <- future::future(
    CachedFit(
        {
            lme4::glmer(y ~ 1 + condition + (1 + condition | id), data = dd, family = 'binomial')
        },
        rds_filename = lme4_fit_2L_fn))

lme4_fit_2L_2rx_fn <- '/data/jflournoy/split/probly/lme4_test_fit_2L_2rx.RDS'
lme4_fit_2L_2rx_future <- future::future(
    CachedFit(
        {
            lme4::glmer(y ~ 1 + condition + (1 + condition | id) + (1 + condition | grp), 
                        data = dd, family = 'binomial')
        },
        rds_filename = lme4_fit_2L_2rx_fn))

summary(glm_fit)

rbind(
    means = unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2]),
    glm_coef = c(coef(glm_fit)[1], sum(coef(glm_fit)[1:2]), sum(coef(glm_fit)[c(1,3)])),
    glm_p = arm::invlogit(c(coef(glm_fit)[1], sum(coef(glm_fit)[1:2]), sum(coef(glm_fit)[c(1,3)]))))

Sys.sleep(3)
if(resolved(lme4_fit_future)){
    lme4_fit <- future::value(lme4_fit_future)
    print(summary(lme4_fit))
    rbind(
        means = unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2]),
        lme4_coef = c(fixef(lme4_fit)[1], sum(fixef(lme4_fit)[1:2]), sum(fixef(lme4_fit)[c(1,3)])),
        lme4_p = arm::invlogit(c(fixef(lme4_fit)[1], sum(fixef(lme4_fit)[1:2]), sum(fixef(lme4_fit)[c(1,3)]))))
    print(
        ggplot2::qplot(as.vector(hyper_gamma_mu),
                       fixef(lme4_fit) + c(0, fixef(lme4_fit)[c(1,1)])) +
        geom_abline(intercept = 0, slope = 1))
    print(
        ggplot2::qplot(as.vector(gamma_mu), 
                   unlist(coef(lme4_fit)$grp+
                              cbind(rep(0, 4),coef(lme4_fit)$grp[,c(1,1)]))) +
        geom_abline(intercept = 0, slope = 1))
    print(
        ggplot2::qplot(as.vector(beta_j), 
                   unlist(coef(lme4_fit)$`id:grp`+
                              cbind(rep(0, dim(beta_j)[1]),coef(lme4_fit)$`id:grp`[,c(1,1)]))) +
        geom_abline(intercept = 0, slope = 1))
}
if(resolved(lme4_fit_2L_future)){
    lme4_fit_2L <- future::value(lme4_fit_2L_future)
    print(summary(lme4_fit_2L))
    rbind(
        means = unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2]),
        lme4_coef = c(fixef(lme4_fit_2L)[1], sum(fixef(lme4_fit_2L)[1:2]), sum(fixef(lme4_fit_2L)[c(1,3)])),
        lme4_p = arm::invlogit(c(fixef(lme4_fit_2L)[1], sum(fixef(lme4_fit_2L)[1:2]), sum(fixef(lme4_fit_2L)[c(1,3)]))))
    print(
        ggplot2::qplot(as.vector(beta_j), 
                   unlist(coef(lme4_fit_2L)$`id`+
                              cbind(rep(0, dim(beta_j)[1]),coef(lme4_fit_2L)$id[,c(1,1)]))) +
        geom_abline(intercept = 0, slope = 1))
}

if(resolved(lme4_fit_2L_2rx_future)){
    lme4_fit_2L_2rx <- future::value(lme4_fit_2L_2rx_future)
    print(summary(lme4_fit_2L_2rx))
    rbind(
        means = unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2]),
        lme4_coef = c(fixef(lme4_fit_2L_2rx)[1], sum(fixef(lme4_fit_2L_2rx)[1:2]), sum(fixef(lme4_fit_2L_2rx)[c(1,3)])),
        lme4_p = arm::invlogit(c(fixef(lme4_fit_2L_2rx)[1], sum(fixef(lme4_fit_2L_2rx)[1:2]), sum(fixef(lme4_fit_2L_2rx)[c(1,3)]))))
    print(
        ggplot2::qplot(as.vector(beta_j), 
                   unlist(coef(lme4_fit_2L_2rx)$`id`+
                              cbind(rep(0, dim(beta_j)[1]),coef(lme4_fit_2L_2rx)$id[,c(1,1)]))) +
        geom_abline(intercept = 0, slope = 1))
}

```

The stan model that is being estimated is:

$$
\text{press_right}_{i} \sim \text{bernoulli_logit}(x_{i}\beta_{jj[i]}) \\
\beta_{j} \sim \mathcal{N}_{\text{mv}}(\delta_{mm[j]}, \Sigma_{\beta})  \\
\Sigma = \text{diag_matrix}(\tau) \Omega \text{diag_matrix}(\tau) \\
\tau_{k} \sim \text{Cauchy}(0, 2.5) \\
\Omega \sim \text{lkj_corr}(2)\\ 
\delta_{mk} \sim \mathcal{N} (\mu_{\delta k}, \sigma_{\delta})  \\
\mu_{\delta} \sim \mathcal{N} (0, 5) \\
\sigma_{\delta} \sim \text{exponential} (1)
$$

Where 
    - press_right is a binary indicator that the participant pressed the key on the right,
    - $x_{i}$ is dummy coded for each trial's condition,
    - $\beta_j$ is a vector of subject-level (for subject $jj[i]$) coefficients for all K conditions,
    - $\delta_m$ is a vector of K means (again, per condition) for participant $j$'s group $mm[j]$,
    - $\Sigma_{\beta}$ is the covariance matrix, optimized as recommended in the stan manual via $\tau$ and $\Omega$,
    - $\mu_{\delta}$ is the population mean for each K condition,
    - and $\sigma_{\delta}$ is the scale parameter for the population means. 

```{r test-stan-mvnorm}
# data {
  # int<lower=1> N; //number of subjects
  # int<lower=1> T; //max number of trials
  # int<lower=2> K; //number of trial predictors (in this case, conditions)
  # int<lower=1> L; //number of subject-level predictors. 1 = intercept only
  # int<lower=1,upper=T> Tsubj[N]; //trials per subject
  # int<lower=-1,upper=1> press_right[N,T]; //choices "0" = left, "1" = right
  # int<lower=-1,upper=3> condition[N,T]; //1 = ctrl, 2 = mateseeking, 3 = status
  # matrix[N, L] u; //group predictors. u[,1] = 1 for intercept
# }
press_right_mat <- matrix(dd$y, nrow = j)
condition_mat <- matrix(as.numeric(dd$condition), nrow = j)
data_for_stan <- list(
    N = j,
    T = t*c,
    K = c,
    M = g,
    mm = gg,
    Tsubj = rep(t*3, j),
    press_right = press_right_mat,
    condition = condition_mat
)

stan_fit_fn.orig <- '/data/jflournoy/split/probly/stan_test_fit_c_l3.RDS'
stan_fit_fn.repar <- '/data/jflournoy/split/probly/stan_test_fit_non_c_l3.RDS'
if(!file.exists(stan_fit_fn.orig)){
    plan(multiprocess)
    stan_m_c <- rstan::stan_model(file = '../exec/splt_rl_mvnorm_test_c_l3.stan')
    stan_optim_c <- rstan::optimizing(stan_m_c,
                                    data = data_for_stan)
    round(stan_optim_c$par[grep('delta', names(stan_optim_c$par))],3)
    stan_fit_test_c_f <- future({rstan::stan(file = '../exec/splt_rl_mvnorm_test_c_l3.stan',
                                             data = data_for_stan, chains = 4, iter = 1500,
                                             warmup = 1000, cores = 4, open_progress = T)})
    stan_fit_test_c <- value(stan_fit_test_c_f)
    saveRDS(stan_fit_test_c, stan_fit_fn.orig)
} else {
    stan_fit_test_c <- readRDS(stan_fit_fn.orig)
}
if(!file.exists(stan_fit_fn.repar)){
    plan(multiprocess)
    stan_m_nc <- rstan::stan_model(file = '../exec/splt_rl_mvnorm_test_non_c_l3.stan')
    stan_optim_nc <- rstan::optimizing(stan_m_nc,
                                    data = data_for_stan)
    round(stan_optim_nc$par[grep('delta', names(stan_optim_nc$par))],3)
    stan_fit_test_nc_f <- future({rstan::stan(file = '../exec/splt_rl_mvnorm_test_non_c_l3.stan',
                                              data = data_for_stan, chains = 4, iter = 1500,
                                              warmup = 1000, cores = 4, open_progress = T)})
    stan_fit_test_nc <- value(stan_fit_test_nc_f)
    saveRDS(stan_fit_test_nc, stan_fit_fn.repar)
} else {
    stan_fit_test_nc <- readRDS(stan_fit_fn.repar)
}

par_names.c <- grep('(delta|beta)', names(stan_fit_test_c), value = T)
par_names.nc <- grep('(delta|beta)', names(stan_fit_test_nc), value = T)
stan_fit_extract.c <- rstan::extract(stan_fit_test_c, pars = par_names.c)
stan_fit_extract.nc <- rstan::extract(stan_fit_test_nc, pars = par_names.nc)
bayesplot::mcmc_dens(as.array(stan_fit_test_c), regex_pars = 'mu_delta\\[\\d\\]')
bayesplot::mcmc_dens(as.array(stan_fit_test_nc), regex_pars = 'mu_delta\\[\\d\\]')
bayesplot::mcmc_trace(as.array(stan_fit_test_c), regex_pars = 'mu_delta\\[\\d\\]')
bayesplot::mcmc_trace(as.array(stan_fit_test_nc), regex_pars = 'mu_delta\\[\\d\\]')
stan_fit_c_means <- lapply(stan_fit_extract.c, mean)
stan_fit_nc_means <- lapply(stan_fit_extract.nc, mean)
print(
    ggplot2::qplot(as.vector(beta_j),
                   as.numeric(
                       stan_fit_c_means[grep('beta\\[', names(stan_fit_c_means))])) +
        geom_abline(intercept = 0, slope = 1))
print(
    ggplot2::qplot(as.vector(beta_j),
                   as.numeric(
                       stan_fit_nc_means[grep('beta\\[', names(stan_fit_nc_means))])) +
        geom_abline(intercept = 0, slope = 1))
print(
    ggplot2::qplot(as.vector(gamma_mu),
                   as.numeric(
                       stan_fit_c_means[grep('delta\\[\\d,', names(stan_fit_c_means))])) +
        geom_abline(intercept = 0, slope = 1))
print(
    ggplot2::qplot(as.vector(gamma_mu),
                   as.numeric(
                       stan_fit_nc_means[grep('delta\\[\\d,', names(stan_fit_nc_means))])) +
        geom_abline(intercept = 0, slope = 1))
rbind(stan = stan_fit_c_means[grep('mu_delta', names(stan_fit_c_means))],
      raw_p = arm::logit(unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2])),
      group_p = apply(gamma_mu, 2, mean))
rbind(stan = stan_fit_nc_means[grep('mu_delta', names(stan_fit_nc_means))],
      raw_p = arm::logit(unlist(dplyr::summarize(dplyr::group_by(dd, condition), mean = mean(y))[,2])),
      group_p = apply(gamma_mu, 2, mean))
stan_fit_c_means$sigma_delta
stan_fit_nc_means$sigma_delta

summary(stan_fit_test_c, pars = grep('delta',par_names.c, value = T), probs = c(.025, .5, .975))$summary
summary(stan_fit_test_nc, pars = grep('delta',par_names.nc, value = T), probs = c(.025, .5, .975))$summary

```

